Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-17 CMSAC_presentation/CMSAC_reveal_js.qmd
Updates

::::::::: columns

::::::: {.column width="40%"}
::: {.fragment}
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
```
:::

::: {.fragment}
```{r}
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
```
:::

::: {.fragment}
```{r}
knitr::include_graphics("jv_girls_basketball.png")
```
:::

::: {.fragment}
```{r}
knitr::include_graphics("five_babies_playing_basketball.png")

@@

::::::: {.column width="60%"}
::: {.fragment}
```{r, out.width="80%"}
knitr::include_graphics("4 bracket good.png")
```
:::
:::::::
:::::::::

@@

## Game Simulation

-   Given the assigned "known strength", $\theta$, we simulate a game using the Bradley-Terry Model

$$\Pr(i > j) = \frac{e^{\theta_i}}{e^{\theta_i} + e^{\theta_j}} = \frac{1}{1+e^{\theta_i - \theta_j}}$$

-   Each competition structure is simulated given the number of teams, $n$, and $\theta$
-   Below is an example of the output from one simulation of a single elimination tournament structure

```{r}
renamed_df <- all_results_norm %>% 
  select(-c(simulation, distribution, seed, teams)) %>%
  rename(theta = true_strength, r = true_rank, r_hat = rank_hat) %>%
  mutate(theta = round(theta,3))

head(renamed_df,8)
```

@@

<!-- I don't know if the references.bib would work here or not -->

>>>>

:::::::::: columns
::::::: {.column width="40%"}
::: fragment
```{r}
knitr::include_graphics("Mens-Basketball-Olympics-Getty-H-2024.jpeg")
```
:::

::: fragment
```{r}
knitr::include_graphics("five_rec_league_men_playing_basketball.png")
```
:::

::: fragment
```{r}
knitr::include_graphics("jv_girls_basketball.png")
```
:::

::: fragment
```{r}
knitr::include_graphics("five_babies_playing_basketball.png")

@@

:::: {.column width="60%"}
::: fragment
```{r, out.width="80%"}
knitr::include_graphics("4 bracket good.png")
```
:::
::::
::::::::::

@@

@@
